Exploring Uncharted Territories - Predicting Activty Cliffs in Structure-Activity Landscapes

### 2012-07-25 paper.tex
updated some figures for datasets

\ctable[cap={}, caption={Datasets considered in this study.},
label={tab:data}]
{lp{0.3\textwidth}rrrrr}
{}
{\FL
Name & Description & Endpoint & ChEMBL AID & Size & $N_{desc}$ & Reference
\ML
Cavalli & \raggedright{Putative hERG inhibitors (via pharmacophore modeling)} & pIC$_{50}$ &  & 30 & 40 &  Ref.~\citen{Cavalli:2002aa} \NN
Costanzo & \raggedright{Thrombin inhibitors} & $\mathrm{IC_{50}}$ & 305283 & 60 & 21 & 
Ref.~\citen{Costanzo:2005uq} \NN
Kalla & \raggedright{A2B adenosine receptor antagonists} & $K_i$ &
364155 & 38 & 10 & Ref.~\citen{Kalla:2006kx} \NN
Dai & \raggedright{RTK inhibitors} & $K_i$ & 429056 & 44 & 12 & Ref.~\citen{Dai:2007kl}
% Mewshaw & \raggedright{ER$\beta$ inhibitors} & $\mathrm{IC_{50}}$ &
% 306229 & 70 & \cite{Mewshaw:2005vf} \NN
\LL}

\ctable[cap={}, caption={Performance metrics for the random forest
  models built for the datasets used in this study. Training RMSE and $R^2$ are
based on out-of-bag data\cite{Breiman:1984aa} and test metrics are based on a separate
hold out set. },
label={tab:rfmodel-results}]
{lrcrrrr}
{
\tnote{Y-range is calculated using the entire dataset for each study.}
}
{\FL
        &         &                      & \multicolumn{2}{c}{Training} & \multicolumn{2}{c}{Test}
\NN
\cmidrule{4-5}  \cmidrule{6-7}
Dataset & Y-range\tmark & Aggregation Function & RMSE & $R^2$ & RMSE & $R^2$   
\ML
Cavalli & 7.21 & $f_{\textrm{diff}}$ & 1.16& 0.54 & 1.07& 0.56\NN
        & & $f_{\textrm{mean}}$      & 1.03& 0.64 & 1.01& 0.58\NN
        & & $f_{\textrm{geom}}$      & 1.07& 0.61 & 1.01& 0.59\NN \NN
Costanzo & 288.03& $f_{\textrm{diff}}$ & 12.88& 0.24 & & \NN
       & & $f_{\textrm{mean}}$ & 13.56& 0.17 & & \NN \NN
Kalla & 88.25 & $f_{\textrm{diff}}$ & 7.51& 0.62 & & \NN
      &  & $f_{\textrm{mean}}$ & 8.26& 0.53  & & \NN \NN
Dai & 32.71 & $f_{\textrm{diff}}$ & 2.60& 0.44 & & \NN
     &   & $f_{\textrm{mean}}$ & 2.67& 0.41  & & 
\LL
}

>>>>

\ctable[cap={}, caption={Datasets considered in this study. $N_{desc}$ is the number of descriptors
  for the dataset after removal of correlated and low-variance descriptors from the original pool of
109 descriptors.},
label={tab:data}]
{lp{0.3\textwidth}rrrrr}
{}
{\FL
Name & Description & Endpoint & ChEMBL AID & Size & $N_{desc}$ & Reference
\ML
Cavalli & \raggedright{Putative hERG inhibitors (via pharmacophore modeling)} & pIC$_{50}$ &  & 30 & 40 &  Ref.~\citen{Cavalli:2002aa} \NN
Costanzo & \raggedright{Thrombin inhibitors} & $\mathrm{IC_{50}}$ & 305283 & 60 & 21 & 
Ref.~\citen{Costanzo:2005uq} \NN
Kalla & \raggedright{A2B adenosine receptor antagonists} & $K_i$ &
364155 & 38 & 10 & Ref.~\citen{Kalla:2006kx} \NN
Dai & \raggedright{RTK inhibitors} & $K_i$ & 429056 & 44 & 12 & Ref.~\citen{Dai:2007kl}
% Mewshaw & \raggedright{ER$\beta$ inhibitors} & $\mathrm{IC_{50}}$ &
% 306229 & 70 & \cite{Mewshaw:2005vf} \NN
\LL}

\ctable[cap={}, caption={Performance metrics for the random forest
  models built for the datasets used in this study. Training RMSE and $R^2$ are
based on out-of-bag data\cite{Breiman:1984aa} and test metrics are based on a separate
hold out set. },
label={tab:rfmodel-results}]
{lrcrrrr}
{
\tnote{Y-range is calculated using the entire dataset for each study.}
}
{\FL
        &         &                      & \multicolumn{2}{c}{Training} & \multicolumn{2}{c}{Test}
\NN
\cmidrule{4-5}  \cmidrule{6-7}
Dataset & Y-range\tmark & Aggregation Function & RMSE & $R^2$ & RMSE & $R^2$   
\ML
Cavalli & 7.21 & $f_{\textrm{diff}}$ & 1.16& 0.54 & 1.07& 0.56\NN
        & & $f_{\textrm{mean}}$      & 1.03& 0.64 & 1.01& 0.58\NN
        & & $f_{\textrm{geom}}$      & 1.07& 0.61 & 1.01& 0.59\NN \NN
%%
Costanzo & 288.03& $f_{\textrm{diff}}$ & 11.99& 0.24 & 17.97& 0.10 \NN
       & & $f_{\textrm{mean}}$         & 12.88& 0.12 & 16.96& 0.20\NN \NN
%%
Kalla & 88.25 & $f_{\textrm{diff}}$ & 8.12& 0.59 & 6.49& 0.57\NN
      &  & $f_{\textrm{mean}}$      & 8.79& 0.52 & 8.00& 0.47\NN \NN
%%
Dai & 32.71 & $f_{\textrm{diff}}$ & 2.49& 0.48 & 3.21& 0.22\NN
     &   & $f_{\textrm{mean}}$    & 2.64& 0.41 & 2.86& 0.37
\LL
}
